---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "Readme_files/",
  eval = FALSE
)
devtools::load_all()
```

[![Actions Status](https://github.com/difuture-lmu/ds.predict.base/workflows/R-CMD-check/badge.svg)](https://github.com/difuture-lmu/ds.predict.base/actions) [![License: LGPL v3](https://img.shields.io/badge/License-LGPL%20v3-blue.svg)](https://www.gnu.org/licenses/lgpl-3.0) [![codecov](https://codecov.io/gh/difuture/ds.predict.base/branch/master/graph/badge.svg?token=OLIPLWDTN5)](https://codecov.io/gh/difuture/ds.predict.base)

# Base Predict Functions for DataSHIELD

The package provides base functionality to push `R` objects to servers using the DataSHIELD](https://www.datashield.ac.uk/) infrastructure for distributed computing. Additionally, it is possible to calculate predictions on the server for a specific model. Combining these allows to push a model from the local machine to all servers running DataSHIELD and predicting on that model with data exclusively hold by the server. The predictions are stored at the server and can be further analysed using the DataSHIELD functionality for non-disclosive analyses.

## Installation

At the moment, there is no CRAN version available. Install the development version from GitHub:

```{r,eval=FALSE}
remotes::install_github("difuture-lmu/ds.predict.base")
```

#### Register assign methods

It is necessary to register the assign methods in the OPAL administration. The assign methods are:

- `decodeBinary`
- `assignPredictModel`

These methods are registered automatically when publishing the package on OPAL (see [`DESCRIPTION`](https://github.com/difuture/ds.predict.base/blob/master/DESCRIPTION)).

Note that the package needs to be installed at both locations, the server and the analysts machine.

## Usage

```{r, results="hide", warnings=FALSE}
library(DSI)
library(DSOpal)
library(DSLite)
library(dsBaseClient)

library(ds.predict.base)

builder = DSI::newDSLoginBuilder()

builder$append(
  server   = "ibe",
  url      = "******",
  user     = "***",
  password = "******",
  table    = "ProVal.KUM"
)

logindata = builder$build()
connections = DSI::datashield.login(logins = logindata, assign = TRUE, symbol = "D",
  opts = list(ssl_verifyhost = 0, ssl_verifypeer = 0))

### Get available tables:
DSI::datashield.symbols(connections)

### Test data with same structure as data on test server:
dat   = cbind(age = sample(20:100, 100L, TRUE), height = runif(100L, 150, 220))
probs = 1 / (1 + exp(-as.numeric(dat %*% c(-3, 1))))
dat   = data.frame(gender = rbinom(100L, 1L, probs), dat)

### Model we want to upload:
mod = glm(gender ~ age + height, family = "binomial", data = dat)

### Upload model to DataSHIELD server
pushObject(connections, mod)

# Check if model "mod" is now available:
DSI::datashield.symbols(connections)

# Check class of uploaded "mod":
ds.class("mod")

# Now predict on uploaded model and data set "D" and store as object "pred":
predictModel(connections, mod, "pred", dat_name = "D")

# Check if prediction "pred" is now available:
DSI::datashield.symbols(connections)

# Summary of "pred":
ds.summary("pred")

# Now assign values with response type "response":
predictModel(connections, mod, "pred", "D", predict_fun = "predict(mod, newdata = D, type = 'response')")
ds.summary("pred")

DSI::datashield.logout(connections)
```

