---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
options(width = 80)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "Readme_files/"
)

pkgs = c("here", "opalr", "DSI", "DSOpal", "dsBaseClient")
for (pkg in pkgs) {
  if (! requireNamespace(pkg, quietly = TRUE))
    install.packages(pkg, repos = c(getOption("repos"), "https://cran.obiba.org"))
}
devtools::install(quiet = TRUE, upgrade = "always")

## Install packages on the DataSHIELD test machine:
base_dir = here::here()
surl     = "https://opal-demo.obiba.org/"
username = "administrator"
password = "password"

opal = opalr::opal.login(username = username, password = password, url = surl)

pkgs = c("dsPredictBase")
for (pkg in pkgs) {
  check1 = opalr::dsadmin.install_github_package(opal = opal, pkg = pkg, username = "difuture-lmu")
  if (! check1)
    stop("[", Sys.time(), "] Was not able to install ", pkg, "!")

  check2 = opalr::dsadmin.publish_package(opal = opal, pkg = pkg)
  if (! check2)
    stop("[", Sys.time(), "] Was not able to publish methods of ", pkg, "!")
}

## Create dummy model:
#local_data1 = read.csv(paste0(base_dir, "/inst/extdata/ds-test-cnsim1.csv"))
#local_data2 = read.csv(paste0(base_dir, "/inst/extdata/ds-test-cnsim2.csv"))
#
#local_data = rbind(local_data1, local_data2)
#local_data$GENDER = as.factor(local_data$GENDER)
#local_data$DIS_CVA = as.factor(local_data$DIS_CVA)
#local_data$DIS_AMI = as.factor(local_data$DIS_AMI)
#local_data$MEDI_LPD = as.factor(local_data$MEDI_LPD)
#
#local_data = na.omit(local_data)

## Train model:
#mod = glm(DIS_DIAB ~ LAB_TSC + LAB_TRIG + LAB_HDL + LAB_GLUC_ADJUSTED + GENDER + DIS_CVA + MEDI_LPD + DIS_AMI, data = local_data, family = binomial())
#p = predict(mod, type = "response")
#mlr::measureAUC(truth = local_data$MEDI_LPD, probabilities = p, positive = 1)
```

[![Actions Status](https://github.com/difuture-lmu/dsPredictBase/workflows/R-CMD-check/badge.svg)](https://github.com/difuture-lmu/dsPredictBase/actions) [![License: LGPL v3](https://img.shields.io/badge/License-LGPL%20v3-blue.svg)](https://www.gnu.org/licenses/lgpl-3.0) [![codecov](https://codecov.io/gh/difuture-lmu/dsPredictBase/branch/main/graph/badge.svg?token=OLIPLWDTN5)](https://codecov.io/gh/difuture-lmu/dsPredictBase)

# Base Predict Functions for DataSHIELD

The package provides base functionality to push `R` objects to servers using the DataSHIELD](https://www.datashield.org/) infrastructure for distributed computing. Additionally, it is possible to calculate predictions on the server for a specific model. Combining these allows to push a model from the local machine to all servers running DataSHIELD and predicting on that model with data exclusively hold by the server. The predictions are stored at the server and can be further analysed using the DataSHIELD functionality for non-disclosive analyses.

## Installation

At the moment, there is no CRAN version available. Install the development version from GitHub:

```{r, eval=FALSE}
remotes::install_github("difuture-lmu/dsPredictBase")
```

#### Register methods

It is necessary to register the assign and aggregate methods in the OPAL administration. These methods are registered automatically when publishing the package on OPAL (see [`DESCRIPTION`](https://github.com/difuture/dsPredictBase/blob/main/DESCRIPTION)).

Note that the package needs to be installed at both locations, the server and the analysts machine.

## Usage

```{r}
library(DSI)
library(DSOpal)
library(dsBaseClient)

library(dsPredictBase)
```

#### Log into DataSHIELD server

```{r}
builder = newDSLoginBuilder()

surl     = "https://opal-demo.obiba.org/"
username = "administrator"
password = "password"

builder$append(
  server   = "ds1",
  url      = surl,
  user     = username,
  password = password,
  table    = "CNSIM.CNSIM1"
)
builder$append(
  server   = "ds2",
  url      = surl,
  user     = username,
  password = password,
  table    = "CNSIM.CNSIM2"
)

connections = datashield.login(logins = builder$build(), assign = TRUE)

### Get available tables:
datashield.symbols(connections)
```

#### Load test model

```{r}
# Model was fitted on the CNSIM data provided by DataSHIELD. The
# response variable is if a patient have had diabetes or not.

load("inst/extdata/mod.Rda")
summary(mod)
```


#### dsPredictBase functionality

Upload model to DataSHIELD server:
```{r}
pushObject(connections, mod)

# Check if model "mod" is now available:
DSI::datashield.symbols(connections)

# Check class of uploaded "mod":
ds.class("mod")
```

Now predict on uploaded model and data set "D" and store as object "pred":
```{r}
predictModel(connections, mod, "pred", "D")

# Check if prediction "pred" is now available:
datashield.symbols(connections)

# Summary of "pred":
ds.summary("pred")
```

Now do the same but assign the values using response type "response":
```{r}
predictModel(connections, mod, "pred", "D", predict_fun = "predict(mod, newdata = D, type = 'response')")
ds.summary("pred")
```

```{r, eval=FALSE}
datashield.logout(connections)
```

## Deploy information:

__Build by `r Sys.info()[["login"]]` (machine `r Sys.info()[["release"]]`) on `r as.character(Sys.time())`.__

This readme is built automatically after each push to the repository. Hence, it also is a test if the functionality of the package works also on the DataSHIELD servers. We also test these functionality in `tests/testthat/test_on_active_server.R`. The system information of the local and remote servers are as followed:


```{r, include=FALSE}
ri_l  = sessionInfo()
ri_ds = datashield.aggregate(connections, quote(getDataSHIELDInfo()))
client_pkgs = c("DSI", "DSOpal", "dsBaseClient", "dsPredictBase")
remote_pkgs = c("dsBase", "resourcer", "dsPredictBase")
```

- Local machine:
    - `R` version: `r ri_l$R.version$version.string`
    - Version of DataSHELD client packages:


```{r, echo=FALSE}
dfv = installed.packages()[client_pkgs, ]
dfv = data.frame(Package = rownames(dfv), Version = unname(dfv[, "Version"]))
knitr::kable(dfv)
```

- Remote DataSHIELD machines:
    - `R` version of `r names(ri_ds)[1]`: `r ri_ds[[1]]$session$R.version$version.string`
    - `R` version of `r names(ri_ds)[2]`: `r ri_ds[[2]]$session$R.version$version.string`
    - Version of server packages:


```{r, echo=FALSE}
dfv = do.call(cbind, lapply(names(ri_ds), function(nm) {
  out = ri_ds[[nm]]$pcks[remote_pkgs, "Version", drop = FALSE]
  colnames(out) = paste0(nm, ": ", colnames(out))
  as.data.frame(out)
}))
dfv = cbind(Package = rownames(dfv), dfv)
rownames(dfv) = NULL
knitr::kable(dfv)
```

```{r, include=FALSE}
datashield.logout(connections)
```
